Childcare while their mom is working

### 2022-04-03 outputs/paper.Rmd

The 1998 Ghana Demographic and Health Survey was a national-level survey carried out in Ghana. It was conducted by the Ghana Statistical Service collaborated with the Macro International Inc. It was designed to collect data on fertility, family planning, and maternal and child health.

The survey frame was created using the list of Enumeration Areas (EAs) with population and household information from the 1984 Population Census. The 1998 GDHS used a two-stage stratified sampling. At the first stage of sampling, 400 EAs were selected using systematic sampling with probability proportional to size where the selected EAs comprised 138 in the urban areas and 262 in the rural areas. A complete household listing operation was then carried out in all the selected EAs to provide a sampling frame for the second stage selection of households. At the second stage of sampling, a systematic sample of 20 households per EA was selected in the Northern, Upper West and Upper East Regions, and 15 households per EA was selected in the other regions.

@@

# plot the bar graph
work_caretaker %>%
  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
  geom_bar(stat = "identity", position="dodge") + 
  theme_minimal() +
  labs(x='Caretaker while at work', y="Percentage (in %)") +
  theme(legend.position='none') +
  coord_flip() + 
  scale_x_discrete(
    labels = 
      c("respondent" = "respondent",
        "partner" = "partner",
        "other_relative" = "relative",
        "neighbor" = "neighbor",
        "hired" = "hired help",
        "child_in_school" = "schooling",
        "other_female_child" = "other female child",
        "other_male_child" = "other male child",
        "not_worked_since_birth" = "not worked since birth",
        "other" = "other",
        "missing" = "missing")
  ) +
  facet_wrap_paginate(vars(background),
                      ncol=2,
                      nrow=2,
                      dir = "h",
                      scales = "free",
                      labeller = labeller(background = c("For_family_member" = "For family member",
                                                         "For_someone_else" = "For someone else",
                                                         "Self-employed" = "Self-employed")
                      )
  )

@@

```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by Occupation", fig.width=6, fig.height=4}
# caretaker aspect
occup_caretaker <-
  occup_long %>%
  filter(str_detect(variable, "^caretaker_")) %>%
  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
  rename(caretaker = variable,
         percentage = count) %>%
  mutate(
    caretaker = factor(caretaker, 
                       levels = c('respondent',
                                  'partner',
                                  'other_relative',
                                  'neighbor',
                                  'hired',
                                  'child_in_school',
                                  'other_female_child',
                                  'other_male_child',
                                  'not_worked_since_birth',
                                  'other',
                                  'missing'))
  )

# plot bar graph
occup_caretaker %>%
  ggplot(aes(x=caretaker, y=percentage, fill=background)) +
  geom_bar(stat = "identity", position="dodge") + 
  labs(x='Caretaker while at work', y="Percentage (in %)", fill="Occupation") +
  theme_minimal() +
  theme(legend.position='bottom') +
  coord_flip() +
  scale_x_discrete(
    labels = 
      c("respondent" = "respondent", 
        "partner" = "partner",
        "other_relative" = "relative",
        "neighbor" = "neighbor",
        "hired" = "hired help",
        "child_in_school" = "schooling",
        "other_female_child" = "other female child",
        "other_male_child" = "other male child",
        "not_worked_since_birth" = "not worked since birth",
        "other" = "other",
        "missing" = "missing")
  )
```

@@

# Discussions

>>>>

The 1998 Ghana Demographic and Health Survey was a national-level survey carried out in Ghana. It was conducted by the Ghana Statistical Service collaborated with the Macro International Inc. It was designed to collect data on fertility, family planning, and maternal and child health. The 1998 GDHS was conducted from mid-November 1998 to mid-February 1999.

The survey frame was created using the list of Enumeration Areas (EAs) with population and household information from the 1984 Population Census. The 1998 GDHS used a two-stage stratified sampling method. At the first stage of sampling, 400 EAs were selected using systematic sampling with probability proportional to size where the selected EAs comprised 138 in the urban areas and 262 in the rural areas. A complete household listing operation was then carried out in all the selected EAs to provide a sampling frame for the second stage selection of households. At the second stage of sampling, a systematic sample of 20 households per EA was selected in the Northern, Upper West and Upper East Regions, and 15 households per EA was selected in the other regions.

The GDHS was composed of 3 parts: the Household's questionnaire, the Woman's questionnaire and the Man's questionnaire. All the questionnaires were modified to account for the situation in Ghana.

@@

# plot the bar graph
work_caretaker %>%
  ggplot(mapping=aes(x=caretaker, y=percentage, fill=caretaker)) +
  geom_bar(stat = "identity", position="dodge") + 
  theme_minimal() +
  labs(x='Caretaker while at work', y="Percent") +
  theme(legend.position='none') +
  coord_flip() + 
  scale_x_discrete(
    labels = 
      c("respondent" = "respondent",
        "partner" = "partner",
        "other_relative" = "relative",
        "neighbor" = "neighbor",
        "hired" = "hired help",
        "child_in_school" = "schooling",
        "other_female_child" = "other female child",
        "other_male_child" = "other male child",
        "not_worked_since_birth" = "not worked since birth",
        "other" = "other",
        "missing" = "missing")
  ) +
  facet_wrap_paginate(vars(background),
                      ncol=2,
                      nrow=2,
                      dir = "h",
                      scales = "free",
                      labeller = labeller(background = c("For_family_member" = "For family member",
                                                         "For_someone_else" = "For someone else",
                                                         "Self-employed" = "Self-employed")
                      )
  )

@@

```{r occupationchildcare, echo=FALSE, fig.cap="Distribution of child's caretaker by occupation", fig.width=6, fig.height=4}
# caretaker aspect
occup_caretaker <-
  occup_long %>%
  filter(str_detect(variable, "^caretaker_")) %>%
  mutate(variable = str_replace_all(variable, "caretaker_", "")) %>%
  rename(caretaker = variable,
         percentage = count) %>%
  mutate(
    caretaker = factor(caretaker, 
                       levels = c('respondent',
                                  'partner',
                                  'other_relative',
                                  'neighbor',
                                  'hired',
                                  'child_in_school',
                                  'other_female_child',
                                  'other_male_child',
                                  'not_worked_since_birth',
                                  'other',
                                  'missing'))
  )

# plot bar graph
occup_caretaker %>%
  ggplot(aes(x=caretaker, y=percentage, fill=background)) +
  geom_bar(stat = "identity", position="dodge") + 
  labs(x='Caretaker while at work', y="Percent", fill="Occupation") +
  theme_minimal() +
  theme(legend.position='bottom') +
  coord_flip() +
  scale_x_discrete(
    labels = 
      c("respondent" = "respondent", 
        "partner" = "partner",
        "other_relative" = "relative",
        "neighbor" = "neighbor",
        "hired" = "hired help",
        "child_in_school" = "schooling",
        "other_female_child" = "other female child",
        "other_male_child" = "other male child",
        "not_worked_since_birth" = "not worked since birth",
        "other" = "other",
        "missing" = "missing")
  )
```

@@

# Discussion
